Linear Variation and an Optimization of Algorithms for Connected Components Labeling in a Binary Image

### 2016-07-31 paper/paper.tex

We present an efficient way to convert the initial binary image with
8-connectivity into a condensed (non-binary) image with new connectivity that is
2 times smaller in each dimension than the initial image. Most approaches for
connected components labeling are still valid for the new image. As time and
memory consumptions of conventional approaches usually depend linearly on the
number of pixels, running them on the condensed image can be more efficient than
running on the initial image. The provided benchmark on random images showed
worst-case speedup factor of $1.7$ for one of our optimizations of the common
SUF approach to CC labeling. The same algorithm is shown to outperform the
previously known decision tree optimization of SUF by at least $1.5$ factor for
image densities less than 80\%.

>>>>

We present an efficient way to convert the initial binary image with
8-connectivity into a smaller condensed image with new connectivity.
Most approaches for connected components labeling are still valid
for the new image. As time and memory complexities of conventional
approaches usually depend linearly on the number of pixels, running
them on the condensed image can be more efficient than
running on the initial image. The provided benchmark on random images showed
worst-case speedup factor of $1.7$ for one of our optimizations of the common
SUF approach to CC labeling. The same algorithm is shown to outperform the
previously known decision tree optimization of SUF by at least $1.5$
factor for images with less than 80\% density.
